%------------------------
% Resume Template
% Author : Brandon Jenniges
% Github : https://github.com/brandonjenniges
% LinkedIn : https://www.linkedin.com/in/bjenniges/
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Brandon Jenniges}} & Email: {hello@brandonjenniges.me}\\
  {LinkedIn: ~~linkedin.com/in/bjenniges/} \\
  {Github: ~~github.com/brandonjenniges} \\
\end{tabular*}

\vspace{10pt}

\noindent\small{Senior iOS engineer with 10+ years of experience building across the spectrum, from being the sole mobile dev at early startups to building payments infrastructure handling millions of transactions. I care about craft, I like hard problems, and I own what I build.}

\vspace{10pt}
\section{Skills Summary}
    \resumeSubHeadingListStart
    \resumeSubItem{Languages}{~~~~~~Swift, Objective-C, Java, Kotlin}
    \resumeSubItem{Frameworks}{~~~~SwiftUI, UIKit, Combine, Async/Await, Core Data, MVVM, XCTest}
    \resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, GitHub Actions, Xcode, Instruments, Datadog, Claude Code, Bazel, Fastlane, REST APIs}
    \resumeSubItem{Platforms}{~~~~~~~iOS, Android}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading{Square (Block)}{Remote}
    {Senior iOS Engineer, Developers Mobile}{Feb 2023 -- Feb 2026}
    \resumeItemListStart
        \resumeItem{Mobile Payments SDK}
          {Developed and maintained features across multiple SDKs used internally by Block and by third-party developers to process millions of payments per week using Square hardware, including offline payment capabilities.}
        \resumeItem{New Payment Method}
          {Led iOS development of a new payment method integrated into the Square Point of Sale app enabling buyers to apply funds from third-party partner programs toward purchases.}
        \resumeItem{Observability Infrastructure}
          {Designed and led the observability architecture for the Mobile Payments SDK, shifting the team from reactive to proactive incident response and enabling confident, reliable rollouts. Significantly reduced on-call response time and served as the blueprint for the Android team.}
        \resumeItem{SwiftUI Adoption}
          {Drove SwiftUI support across SDKs, ran internal training sessions, and paired with teammates to accelerate adoption of modern UI patterns.}
        \resumeItem{Agentic AI Workflows}
          {Served as AI Champion for the team, pioneering agentic development workflows using Claude Code and git worktrees to parallelize tasks and increase development velocity. Mentored teammates on adopting these workflows.}
    \resumeItemListEnd

    \resumeSubheading{GameStop}{Remote}
    {Senior iOS Blockchain Engineer}{Feb 2022 -- Dec 2022}
    \resumeItemListStart
        \resumeItem{GameStop Wallet}
          {Built functionality for the iOS Wallet app including viewing, sending, and managing ERC-20 tokens and NFTs on Ethereum mainnet and Layer 2 networks.}
        \resumeItem{Architecture Modernization}
          {Led efforts to modernize app architecture using SwiftUI, Combine, and Async/Await, mentoring junior engineers on modern iOS development practices.}
        \resumeItem{Testing Standards}
          {Established best practices for unit and UI testing using XCTest, laying the foundation for a more reliable and maintainable codebase.}
    \resumeItemListEnd

    \resumeSubheading{Microsoft}{Remote}
    {Software Engineer 2}{Dec 2020 -- Feb 2022}
    \resumeItemListStart
        \resumeItem{Activity Feed}
          {Served as iOS DRI for the activity feed feature, collaborating with Android and server teams to ship real-time in-app notifications for comments, likes, and video activity to millions of users.}
        \resumeItem{SwiftUI and Accessibility}
          {Established team best practices for SwiftUI and Combine. Ensured the app adhered to strict accessibility standards to maximize reach and usability.}
    \resumeItemListEnd

    \resumeSubheading{Bleachr, LLC}{Minneapolis, MN}
    {Senior Mobile Software Engineer / Lead Mobile Design Architect}{Apr 2016 -- Dec 2020}
    \resumeItemListStart
        \resumeItem{TennisONE and Bleachr}
          {Led iOS development of the TennisONE and Bleachr apps, driving key features including a rewards store, in-seat ordering, and home screen feed across a growing mobile team.}
    \resumeItemListEnd

    \resumeSubheading{Jump Technologies, Inc.}{Minneapolis, MN}
    {Mobile Software Engineer}{May 2015 -- Apr 2016}
    \resumeItemListStart
        \resumeItem{iOS and Android Development}
          {Built and maintained iOS and Android features for enterprise mobile applications as the sole mobile developer.}
    \resumeItemListEnd

    \resumeSubheading{Menards, Inc.}{Eau Claire, WI}
    {Mobile Software Engineer}{Sep 2013 -- May 2015}
    \resumeItemListStart
        \resumeItem{iOS and Android Development}
          {Contributed to iOS and Android application development for internal store operations at one of the largest home improvement retailers in the US.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\vspace{-5pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Southwest Minnesota State University}{}
      {B.S. in Computer Science}{Jan 2010 -- Dec 2013}
  \resumeSubHeadingListEnd

\end{document}
